CSci487 Penetration Testing Project: AILEE

### 2019-05-06 csci487/project/paper.tex
Ooopsie
Signed-off-by: Grant Haataja <grant.haataja@gmail.com>

The user is encouraged to try out the various possible commands, which can be displayed using the \textit{help} command. The story continues after the user has ran ten commands, (they can be the same or different commands, it doesn't matter).

@@

Above is the code for the \textit{exploit} command in the game. In terms of options, it does not compare to the Metasploit framework, but the goal was to create it to feel similarly in the terminal environment.

\begin{figure}[h]
	\centerline{\includegraphics[scale=2]{exploit-pic}}
	\caption{Running the \textit{exploit} executable}
	\label{fig:exploit-pic}
\end{figure}

@@

The story development of the game is controlled by event scripts that are triggered at specific times. Running the events in the proper order is critical for the game to play as planned. The first event is run immediately after the game loads its first shell on the localhost computer. Each event after that has a condition that must be met to trigger it. The second event runs after ten commands have been run, the third event runs after the \textit{pscan} command runs, and so on. Each event runs instructions for the user that should allow them to trigger the next event and progress in the game.

@@

This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \textit{pscan} against the first target IP address.

@@

\subsection{Computers and Filesystems}
AILEE uses a filesystem structure that feels like a Linux terminal. There are a total of four computers in the game, localhost (AILEE's home computer), the two targets, and one other computer. Each computer has a unique filesystem, with directories and files. As time was limited, the \textit{bin} and \textit{log} directories were left empty on all computers, but the \textit{home} directories all have files in them that either pertain to the gameplay or exist for comedic value or storyline development.

To navigate the filesystems, the traditional Linux commands \textit{ls} and \textit{cd} are used, as well as the commands \textit{read} and \textit{run}, which display file text and run executable files, respectively.

@@

Directories are colored light blue, executables are light green, and regular files are white (Fig. \ref{fig:ls-command}). Unlike a real Linux terminal, the \textit{ls} command only works in the current directory and takes no arguments.

>>>>

The user is encouraged to try out the various possible commands, which can be displayed using the \texttt{help} command. The story continues after the user has ran ten commands, (they can be the same or different commands, it doesn't matter).

@@

Above is the code for the \texttt{exploit} command in the game. In terms of options, it does not compare to the Metasploit framework, but the goal was to create it to feel similarly in the terminal environment.

\begin{figure}[h]
	\centerline{\includegraphics[scale=2]{exploit-pic}}
	\caption{Running the \texttt{exploit} executable}
	\label{fig:exploit-pic}
\end{figure}

@@

The story development of the game is controlled by event scripts that are triggered at specific times. Running the events in the proper order is critical for the game to play as planned. The first event is run immediately after the game loads its first shell on the localhost computer. Each event after that has a condition that must be met to trigger it. The second event runs after ten commands have been run, the third event runs after the \texttt{pscan} command runs, and so on. Each event runs instructions for the user that should allow them to trigger the next event and progress in the game.

@@

This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \texttt{pscan} against the first target IP address.

@@

\subsection{Computers and Filesystems}
AILEE uses a filesystem structure that feels like a Linux terminal. There are a total of four computers in the game, localhost (AILEE's home computer), the two targets, and one other computer. Each computer has a unique filesystem, with directories and files. As time was limited, the \texttt{bin} and \texttt{log} directories were left empty on all computers, but the \texttt{home} directories all have files in them that either pertain to the gameplay or exist for comedic value or storyline development.

To navigate the filesystems, the traditional Linux commands \texttt{ls} and \texttt{cd} are used, as well as the commands \texttt{read} and \texttt{run}, which display file text and run executable files, respectively.

@@

Directories are colored light blue, executables are light green, and regular files are white (Fig. \ref{fig:ls-command}). Unlike a real Linux terminal, the \texttt{ls} command only works in the current directory and takes no arguments.
